### 2022-11-30 chapter1/chapter1.tex
Fixed bad figure reference
Minor wording change in refinement methods
Removed reference to first stage since second stage is not referenced in method

After the model was trained on manually labeled examples, it was used to assign a label to the columns in each alignment. Columns assigned to states 1A and 1B are the regions of interest for downstream analyses since the gaps generally follow the expected pattern given the phylogenetic tree. In contrast, columns assigned to states 2 and 3 largely corresponded to the long poorly supported segments and phylogenetically discordant regions discussed previously and were therefore removed from the alignments. In the example decoded alignment shown, the decoded states closely follow the expected patterns (Fig.~ref{fig:hmm})B). Overall, fewer than 10\% of alignments were trimmed of any regions. However, when regions were trimmed, they were largely inferred as state 3, meaning the removed regions are generally long poorly supported segments that are aligned to few if any other sequences (Fig.~\ref{sfig:hmm_trim}).

@@

\subsection*{Alignment refinement}
In the first stage, the representative sequences in the single copy orthologous groups were aligned with the same settings as described in the previous section, except \textit{a\textsubscript{max}} was set to 0.7. A binary profile was created from the alignment using Gaussian process sequence weighting as described in the previous section. (Because the orthologous groups were single copy and contained only representative sequences, each sequence received the full weight associated with its species.) The binary profile was then converted into a binary mask by identifying where the weighted fraction of non-gap symbols exceeded 0.5. The binary mask was closed with a structuring element of size three, and highly conserved regions were identified as the contiguous intervals of this closed mask with a minimum length of 10. Diverged regions were taken as the complement of the highly conserved regions. For each diverged region, the corresponding segments of the sequences in the initial alignment were extracted and aligned with \textit{a\textsubscript{max}} set to 0.4. The resulting sub-alignments were then stitched into the initial alignment.

>>>>

After the model was trained on manually labeled examples, it was used to assign a label to the columns in each alignment. Columns assigned to states 1A and 1B are the regions of interest for downstream analyses since the gaps generally follow the expected pattern given the phylogenetic tree. In contrast, columns assigned to states 2 and 3 largely corresponded to the long poorly supported segments and phylogenetically discordant regions discussed previously and were therefore removed from the alignments. In the example decoded alignment shown, the decoded states closely follow the expected patterns (Fig.~\ref{fig:hmm}B). Overall, fewer than 10\% of alignments were trimmed of any regions. However, when regions were trimmed, they were largely inferred as state 3, meaning the removed regions are generally long poorly supported segments that are aligned to few if any other sequences (Fig.~\ref{sfig:hmm_trim}).

@@

\subsection*{Alignment refinement}
The representative sequences in the single copy orthologous groups were aligned with the same settings as described in the previous section except \textit{a\textsubscript{max}} was set to 0.7. A binary profile was created from the alignment using Gaussian process sequence weighting as described in the previous section. (Because the orthologous groups were single copy and contained only representative sequences, each sequence received the full weight associated with its species.) The binary profile was then converted into a binary mask by identifying where the weighted fraction of non-gap symbols exceeded 0.5. The binary mask was closed with a structuring element of size three, and highly conserved regions were identified as the contiguous intervals of this closed mask with a minimum length of 10. Diverged regions were taken as the complement of the highly conserved regions. For each diverged region, the corresponding segments of the sequences in the initial alignment were extracted and aligned with \textit{a\textsubscript{max}} set to 0.4. The resulting sub-alignments were then stitched into the initial alignment.
